---
title: "Caribou Population Growth Model: SpaDES Module"
author: "Tati Micheletti & Frances Stewart"
date: "15 February 2019"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = FALSE, echo = TRUE, eval = FALSE)
```

This module uses the coefficients for recruitment and survival of Woodland Boreal Caribou in Canada to forecast population growth rates into the future. Two models can be chosen for recruitment and survival: published ECCC (2011) or Johnson et al., (2020).

# Usage

```{r module_usage}
require("Require")
Require("testthat")
Require("SpaDES")
Require("raster")

# Check current directory. It needs to be the toplevel of the module
message(paste0("Your working directory is ", getwd()))
testthat::expect_true(basename(getwd()) == "caribouPopGrowthModel", 
                      label = paste0("To use this module, please make sure your current directory ",
       "is the top level of the module 'caribouPopGrowthModel'. You can",
       " do this by either using setwd('~/caribouPopGrowthModel') or by",
       " opening (double-clicking) the caribouPopGrowthModel.Rproj file. "))

# Source functions in R folder
invisible(sapply(X = list.files(file.path(getwd(), "R"), 
                                full.names = TRUE), FUN = source))

# Set a storage project folder
message(paste0("Your current temporary directory is ", tempdir()))

setPaths(modulePath = dirname(getwd()),
         inputPath = file.path(getwd(), "inputs"), 
         outputPath = file.path(getwd(), "outputs"), 
         cachePath = file.path(getwd(), "cache"))
getPaths() # shows where the 4 relevant paths are

times <- list(start = 2011, end = 2100)
params <- list(
  "caribouPopGrowthModel" = list(
    ".growthInterval" = 10
  )
)

if (quickPlot::isRstudioServer()) options(httr_oob_default = TRUE)

caribous <- simInitAndSpades(times = times, 
                             params = params, 
                             outputs =  data.frame(objectName = c("disturbances",
                                                                  "predictedCaribou"),
                                                   saveTime = times$end),
                             modules = list("caribouPopGrowthModel"),
                             objects = list())
```

# Events

1. makingModel: Uses the function `createModels(caribouCoefTable, modelsToUse)` to create a `data.table` using the coefficients from one of the specific models coming from ECCC 2012 report.   

2. gettingData:  looks for landscape maps (two objects: `pixelGroupMap` and `cohortData`) using the function `createModObject()` either in the `simList` or in the `inputPath()`. These are the objects that will be used for calculating the model parameters.  

3. growingCaribou: resolves the mathematical equation of the model and using a recruitment-habitat relationship, calculates lambda.     

4. plot: described below

## Plotting

In the last year of the simulation, the module plots lambda through time

## Input data

    waterRaster: RasterLayer
                 desription: Wetland raster for excluding water from anthropogenic layer
    caribouArea1: SpatialPolygonsDataFrame
                 desription: Study area to predict caribou population to (NWT_Regions_2015_LCs_DC_SS)
                 sourceURL = "https://drive.google.com/open?id=1Qbt2pOvC8lGg25zhfMWcc3p6q3fZtBtO"),
    Edehzhie: SpatialPolygonsDataFrame
                 desription: Study area to predict caribou pospulation to
                 sourceURL = "https://drive.google.com/open?id=1VP91AyIeGCFwJS9oPSEno4_SbtJQJMh7"),
    caribouArea2: SpatialPolygonsDataFrame
                 desription: Study area to predict caribou population to (NT1_BOCA_spatial_units_for_landscape)
                 sourceURL = "https://drive.google.com/open?id=1Vqny_ZMoksAjji4upnr3OiJl2laGeBGV"),
    currentPop: numeric 
                 desription: Caribou population size in the study area. Is updated every time step
    adultFemaleSurv: numeric 
                 desription: Caribou female survival probability in the study area. Default of 0.85
    pixelGroupMap: RasterLayer
                 desription: Map of groups of pixels that share the same info from cohortData (sp, age, biomass, etc).
                 Should at some point be genrated by the fire model (i.e. scfmSpread)
    cohortData: data.table
                 desription: data.table with information by pixel group of sp, age, biomass, etc
    anthropogenicLayer: RasterLayer
                 desription: Layer that maps the % of anthropogenic disturbance of in each pixel. 
                               "This layer is static if no modules are forecasting anthropogenic disturbances
    modelsToUse: character 
                 desription: Which models from ECCC to be used?
    caribouData: data.table 
                 desription: Data containing recruitment and other pop covariates 
                 sourceURL = "https://drive.google.com/open?id=1SOimSD2jehRxV-SbMmgLUh3W5yStwhdq
    provinces: character 
                 desription: Which province caribou data should be used for the module?"),
    caribouCoefTable: data.table 
                 desription: Published caribou coefficients 
                 sourceURL = "https://drive.google.com/open?id=14ck35G8A3A6s65vSAWWeUp2_vXgmYZe5

## Output data

    caribouModels: list
                 description: List with model equations. Default is M3 (ECCC 2011, Table 56) downloaded if needed.
    predictedCaribou: list
                  description: Data.table that contains the total population size per year, as well as other parameters
    currentPop: numeric
                  description: Caribou population size in the study area. Is updated every time step
    plotCaribou: ggplot2
                  description: Caribou population size through time
    disturbances: list
                  description: disturbances is a list of shapefiles that have polygons with 
                                the total disturbance in the area in percentage.
                                If not provided, it is created from sim$rstCurrentBurn
                                coming from scfmSpread.
    listSACaribou: list
                  description: List of caribou areas to predict for
                                Currently only takes 3 shapefiles

# Links to other modules

This module needs to be linked to a vegetation and disturbance modules that generate pixelGroupMap maps and cohortData tables. Otherwise, there is the need for a translation module from disturbance map outputs.

# Link to the the SpaDES module's R script

[Here is the SpaDES module's R script](https://github.com/tati-micheletti/caribouPopGrowthModel/blob/master/caribouPopGrowthModel.R)

