---
title: "caribouPopGrowthModel"
author: ''
date: "15 February 2019"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = FALSE, echo = TRUE, eval = FALSE)
```

# Usage

```{r module_usage}
# Load SpaDES
setwd("/mnt/data/Micheletti/NWT")
library("SpaDES")
library("raster")

# Source functions in R folder
invisible(sapply(X = list.files(file.path(getwd(), "R"), full.names = TRUE), FUN = source))
invisible(sapply(X = list.files(file.path(dirname(dirname(getwd())), "functions"), full.names = TRUE), FUN = source))

# Set a storage project folder
workDirectory <- getwd()
message("Your current temporary directory is  tempdir()")

setPaths(modulePath = file.path(getwd(), "modules"), 
         inputPath = file.path("/mnt/data/Micheletti/NWT/outputs/10JUL19/"), 
         outputPath = file.path("/mnt/data/Micheletti/NWT/outputs/10JUL19/PopGrowth/"), 
         cachePath = file.path("/mnt/data/Micheletti/NWT/cache/"))
getPaths() # shows where the 4 relevant paths are


times <- list(start = 2001, end = 2100)

parameters <- list(
  caribouPopGrowthModel = list(
    ".plotInitialTime" = NULL,
    "recoveryTime" = 40,
    ".useDummyData" = FALSE,
    ".growthInterval" = 5)
)
modules <- list("caribouPopGrowthModel")
objects <- list()
inputs <- list()
outputs <- list()

if (quickPlot::isRstudioServer()) options(httr_oob_default = TRUE)

caribous <- simInitAndSpades(times = times, params = parameters, modules = modules,
                 objects = objects)

```

# Events

1. makingModel: Uses the function `createModels(caribouCoefTable, modelsToUse)` to create a `data.table` using the coefficients from one of the specific models coming from ECCC 2012 report.   

2. gettingData:  looks for landscape maps (two objects: `pixelGroupMap` and `cohortData`) using the function `createModObject()` either in the `simList` or in the `inputPath()`. These are the objects that will be used for calculating the model parameters.  

3. growingCaribou: resolves the mathematical equation of the model and using a recruitment-habitat relationship, calculates lambda.     

4. plot: described below

## Plotting

In the last year of the simulation, the module plots lambda through time

## Input data

    waterRaster: RasterLayer
                 desription: Wetland raster for excluding water from anthropogenic layer
    caribouArea1: SpatialPolygonsDataFrame
                 desription: Study area to predict caribou population to (NWT_Regions_2015_LCs_DC_SS)
                 sourceURL = "https://drive.google.com/open?id=1Qbt2pOvC8lGg25zhfMWcc3p6q3fZtBtO"),
    Edehzhie: SpatialPolygonsDataFrame
                 desription: Study area to predict caribou pospulation to
                 sourceURL = "https://drive.google.com/open?id=1VP91AyIeGCFwJS9oPSEno4_SbtJQJMh7"),
    caribouArea2: SpatialPolygonsDataFrame
                 desription: Study area to predict caribou population to (NT1_BOCA_spatial_units_for_landscape)
                 sourceURL = "https://drive.google.com/open?id=1Vqny_ZMoksAjji4upnr3OiJl2laGeBGV"),
    currentPop: numeric 
                 desription: Caribou population size in the study area. Is updated every time step
    adultFemaleSurv: numeric 
                 desription: Caribou female survival probability in the study area. Default of 0.85
    pixelGroupMap: RasterLayer
                 desription: Map of groups of pixels that share the same info from cohortData (sp, age, biomass, etc).
                 Should at some point be genrated by the fire model (i.e. scfmSpread)
    cohortData: data.table
                 desription: data.table with information by pixel group of sp, age, biomass, etc
    anthropogenicLayer: RasterLayer
                 desription: Layer that maps the % of anthropogenic disturbance of in each pixel. 
                               "This layer is static if no modules are forecasting anthropogenic disturbances
    modelsToUse: character 
                 desription: Which models from ECCC to be used?
    caribouData: data.table 
                 desription: Data containing recruitment and other pop covariates 
                 sourceURL = "https://drive.google.com/open?id=1SOimSD2jehRxV-SbMmgLUh3W5yStwhdq
    provinces: character 
                 desription: Which province caribou data should be used for the module?"),
    caribouCoefTable: data.table 
                 desription: Published caribou coefficients 
                 sourceURL = "https://drive.google.com/open?id=14ck35G8A3A6s65vSAWWeUp2_vXgmYZe5

## Output data

    caribouModels: list
                 description: List with model equations. Default is M3 (ECCC 2011, Table 56) downloaded if needed.
    predictedCaribou: list
                  description: Data.table that contains the total population size per year, as well as other parameters
    currentPop: numeric
                  description: Caribou population size in the study area. Is updated every time step
    plotCaribou: ggplot2
                  description: Caribou population size through time
    disturbances: list
                  description: disturbances is a list of shapefiles that have polygons with 
                                the total disturbance in the area in percentage.
                                If not provided, it is created from sim$rstCurrentBurn
                                coming from scfmSpread.
    listSACaribou: list
                  description: List of caribou areas to predict for
                                Currently only takes 3 shapefiles

# Links to other modules

This module needs to be linked to a vegetation and disturbance modules that generate pixelGroupMap maps and cohortData tables. Otherwise, there is the need for a translation module from disturtance map outputs.

